---
title: "vast_kallisto_majiq"
output: html_document
---

```{r}
library(tidyverse)
```

the unfortunate part of this is that for each program, each comparison has its own output file (in fact it likely came from its own script too). So this will have to start with a great deal of reading in files and smooshing them together, while making sure we retain all the important details. It might be easiest to do this one program at a time.

ok, so steps:
1. read in all the genes from each program and in each comparison
2. create a list of unique dAS genes in each comparison
3. assign each of these genes a column for the program(s) to which it belongs. can probably use case_when for this (or if-else, thinking of: mutate (if else gene in program_list, program name, NA))
4. join the program name columns together, see test code

```{r}
test <- tibble(x = c("a", "b", NA), y = c("c", NA, "d"), z = c(NA, "e", "f"))
test2 <- test %>% unite(all, c(x, y, z), na.rm = T) #can specify sep as well if you want
```


vast-tools:
```{r}
vast_k20dk20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20d-K20w_68events/K20d-K20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20dK20w"))

vast_k20dl20d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20d-L20d_327events/K20d-L20d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20dL20d"))

vast_k20wl20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20w-L20w_196events/K20w-L20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20wL20w"))

vast_k40dk40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40d-K40w_23events/K40d-K40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40dK40w"))

vast_k40dl40d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40d-L40d_168events/K40d-L40d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40dL40d"))

vast_k40wl40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40w-L40w_69events/K40w-L40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40wL40w"))

vast_k60dk60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60d-K60w_6events/K60d-K60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60dK60w"))

vast_k60dl60d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60d-L60d_94events/K60d-L60d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60dL60d"))

vast_k60wl60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60w-L60w_58events/K60w-L60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60wL60w"))

vast_l20dl20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L20d-L20w_706events/L20d-L20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L20dL20w"))

vast_l40dl40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L40d-L40w_27events/L40d-L40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L40dL40w"))

vast_l60dl60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L60d-L60w_5events/L60d-L60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L60dL60w"))
```

kallisto:
```{r}
kallisto_k20dk20w <- read_delim("../../kallisto/dAS_analysis/dAS_K20dK20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20dK20w"))

kallisto_k40dk40w <- read_delim("../../kallisto/dAS_analysis/dAS_K40dK40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40dK40w"))

kallisto_k60dk60w <- read_delim("../../kallisto/dAS_analysis/dAS_K60dK60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60dK60w"))

kallisto_l20dl20w <- read_delim("../../kallisto/dAS_analysis/dAS_L20dL20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L20dL20w"))

kallisto_l40dl40w <- read_delim("../../kallisto/dAS_analysis/dAS_L40dL40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L40dL40w"))

kallisto_l60dl60w <- read_delim("../../kallisto/dAS_analysis/dAS_L60dL60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L60dL60w"))

kallisto_k20dl20d <- read_delim("../../kallisto/dAS_analysis/dAS_K20dL20d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20dL20d"))

kallisto_k40dl40d <- read_delim("../../kallisto/dAS_analysis/dAS_K40dL40d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40dL40d"))

kallisto_k60dl60d <- read_delim("../../kallisto/dAS_analysis/dAS_K60dL60d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60dL60d"))

kallisto_k20wl20w <- read_delim("../../kallisto/dAS_analysis/dAS_K20wL20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20wL20w"))

kallisto_k40wl40w <- read_delim("../../kallisto/dAS_analysis/dAS_K40wL40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40wL40w"))

kallisto_k60wl60w <- read_delim("../../kallisto/dAS_analysis/dAS_K60wL60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60wL60w"))
```

majiq:
```{r}
majiq_k20dk20w <- read_delim("filter25/K20dK20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20dK20w"))

majiq_k40dk40w <- read_delim("filter25/K40dK40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40dK40w"))

majiq_k60dk60w <- read_delim("filter25/K60dK60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60dK60w"))

majiq_l20dl20w <- read_delim("filter25/L20dL20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L20dL20w"))

majiq_l40dl40w <- read_delim("filter25/L40dL40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L40dL40w"))

majiq_l60dl60w <- read_delim("filter25/L60dL60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L60dL60w"))

majiq_k20dl20d <- read_delim("filter25/K20dL20d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20dL20d"))

majiq_k40dl40d <- read_delim("filter25/K40dL40d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40dL40d"))

majiq_k60dl60d <- read_delim("filter25/K60dL60d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60dL60d"))

majiq_k20wl20w <- read_delim("filter25/K20wL20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20wL20w"))

majiq_k40wl40w <- read_delim("filter25/K40wL40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40wL40w"))

majiq_k60wl60w <- read_delim("filter25/K60wL60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60wL60w"))
```

step2: create a list of unique genes in each comparison
```{r}
K20dK20w <- unique(c(vast_k20dk20w$GeneID, kallisto_k20dk20w$gene_id, majiq_k20dk20w$`Gene ID`))
K40dK40w <- unique(c(vast_k40dk40w$GeneID, kallisto_k40dk40w$gene_id, majiq_k40dk40w$`Gene ID`))
K60dK60w <- unique(c(vast_k60dk60w$GeneID, kallisto_k60dk60w$gene_id, majiq_k60dk60w$`Gene ID`))

L20dL20w <- unique(c(vast_l20dl20w$GeneID, kallisto_l20dl20w$gene_id, majiq_l20dl20w$`Gene ID`))
L40dL40w <- unique(c(vast_l40dl40w$GeneID, kallisto_l40dl40w$gene_id, majiq_l40dl40w$`Gene ID`))
L60dL60w <- unique(c(vast_l60dl60w$GeneID, kallisto_l60dl60w$gene_id, majiq_l60dl60w$`Gene ID`))

K20dL20d <- unique(c(vast_k20dl20d$GeneID, kallisto_k20dl20d$gene_id, majiq_k20dl20d$`Gene ID`))
K40dL40d <- unique(c(vast_k40dl40d$GeneID, kallisto_k40dl40d$gene_id, majiq_k40dl40d$`Gene ID`))
K60dL60d <- unique(c(vast_k60dl60d$GeneID, kallisto_k60dl60d$gene_id, majiq_k60dl60d$`Gene ID`))

K20wL20w <- unique(c(vast_k20wl20w$GeneID, kallisto_k20wl20w$gene_id, majiq_k20wl20w$`Gene ID`))
K40wL40w <- unique(c(vast_k40wl40w$GeneID, kallisto_k40wl40w$gene_id, majiq_k40wl40w$`Gene ID`))
K60wL60w <- unique(c(vast_k60wl60w$GeneID, kallisto_k60wl60w$gene_id, majiq_k60wl60w$`Gene ID`))
```

step3: assign each gene a column for the program(s) to which it belongs and step 4: join program columns together
```{r}
#this may objectively be some of the ugliest code I've ever written... find a way to clean this up!
K20dK20w <- as.data.frame(K20dK20w)
colnames(K20dK20w) <- "gene"
K20dK20w <- K20dK20w %>% mutate(prog1 = if_else(gene %in% vast_k20dk20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20dk20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20dk20w$`Gene ID`, "majiq", "NA")) 
K20dK20w[K20dK20w == "NA"] = NA
K20dK20w <- unite(K20dK20w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20dK20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K40dK40w <- as.data.frame(K40dK40w)
colnames(K40dK40w) <- "gene"
K40dK40w <- K40dK40w %>% mutate(prog1 = if_else(gene %in% vast_k40dk40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40dk40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40dk40w$`Gene ID`, "majiq", "NA")) 
K40dK40w[K40dK40w == "NA"] = NA
K40dK40w <- unite(K40dK40w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40dK40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K60dK60w <- as.data.frame(K60dK60w)
colnames(K60dK60w) <- "gene"
K60dK60w <- K60dK60w %>% mutate(prog1 = if_else(gene %in% vast_k60dk60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60dk60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60dk60w$`Gene ID`, "majiq", "NA")) 
K60dK60w[K60dK60w == "NA"] = NA
K60dK60w <- unite(K60dK60w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60dK60w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

L20dL20w <- as.data.frame(L20dL20w)
colnames(L20dL20w) <- "gene"
L20dL20w <- L20dL20w %>% mutate(prog1 = if_else(gene %in% vast_l20dl20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l20dl20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l20dl20w$`Gene ID`, "majiq", "NA")) 
L20dL20w[L20dL20w == "NA"] = NA
L20dL20w <- unite(L20dL20w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("L20dL20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

L40dL40w <- as.data.frame(L40dL40w)
colnames(L40dL40w) <- "gene"
L40dL40w <- L40dL40w %>% mutate(prog1 = if_else(gene %in% vast_l40dl40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l40dl40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l40dl40w$`Gene ID`, "majiq", "NA")) 
L40dL40w[L40dL40w == "NA"] = NA
L40dL40w <- unite(L40dL40w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("L40dL40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

L60dL60w <- as.data.frame(L60dL60w)
colnames(L60dL60w) <- "gene"
L60dL60w <- L60dL60w %>% mutate(prog1 = if_else(gene %in% vast_l60dl60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l60dl60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l60dl60w$`Gene ID`, "majiq", "NA")) 
L60dL60w[L60dL60w == "NA"] = NA
L60dL60w <- unite(L60dL60w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("L60dL60w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K20dL20d <- as.data.frame(K20dL20d)
colnames(K20dL20d) <- "gene"
K20dL20d <- K20dL20d %>% mutate(prog1 = if_else(gene %in% vast_k20dl20d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20dl20d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20dl20d$`Gene ID`, "majiq", "NA")) 
K20dL20d[K20dL20d == "NA"] = NA
K20dL20d <- unite(K20dL20d, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20dL20d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K40dL40d <- as.data.frame(K40dL40d)
colnames(K40dL40d) <- "gene"
K40dL40d <- K40dL40d %>% mutate(prog1 = if_else(gene %in% vast_k40dl40d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40dl40d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40dl40d$`Gene ID`, "majiq", "NA")) 
K40dL40d[K40dL40d == "NA"] = NA
K40dL40d <- unite(K40dL40d, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40dL40d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K60dL60d <- as.data.frame(K60dL60d)
colnames(K60dL60d) <- "gene"
K60dL60d <- K60dL60d %>% mutate(prog1 = if_else(gene %in% vast_k60dl60d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60dl60d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60dl60d$`Gene ID`, "majiq", "NA")) 
K60dL60d[K60dL60d == "NA"] = NA
K60dL60d <- unite(K60dL60d, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60dL60d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K20wL20w <- as.data.frame(K20wL20w)
colnames(K20wL20w) <- "gene"
K20wL20w <- K20wL20w %>% mutate(prog1 = if_else(gene %in% vast_k20wl20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20wl20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20wl20w$`Gene ID`, "majiq", "NA")) 
K20wL20w[K20wL20w == "NA"] = NA
K20wL20w <- unite(K20wL20w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20wL20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K40wL40w <- as.data.frame(K40wL40w)
colnames(K40wL40w) <- "gene"
K40wL40w <- K40wL40w %>% mutate(prog1 = if_else(gene %in% vast_k40wl40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40wl40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40wl40w$`Gene ID`, "majiq", "NA")) 
K40wL40w[K40wL40w == "NA"] = NA
K40wL40w <- unite(K40wL40w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40wL40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)

K60wL60w <- as.data.frame(K60wL60w)
colnames(K60wL60w) <- "gene"
K60wL60w <- K60wL60w %>% mutate(prog1 = if_else(gene %in% vast_k60wl60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60wl60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60wl60w$`Gene ID`, "majiq", "NA")) 
K60wL60w[K60wL60w == "NA"] = NA
K60wL60w <- unite(K60wL60w, prog, c(prog1, prog2, prog3), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60wL60w")) %>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F)
```

step5: rbind, group_by, summarize and plot!
```{r}
order <- c("K20dK20w", "K40dK40w", "K60dK60w", "L20dL20w", "L40dL40w", "L60dL60w", "K20dL20d", "K40dL40d", "K60dL60d", "K20wL20w", "K40wL40w", "K60wL60w")

all <- rbind(K20dK20w, K40dK40w, K60dK60w, L20dL20w, L40dL40w, L60dL60w, K20dL20d, K40dL40d, K60dL60d, K20wL20w, K40wL40w, K60wL60w)
to_plot <- all %>% group_by(prog, comp, prog_vm) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)

```

```{r}
png("test.png", units="in", width=15, height=8, res=300)
ggplot(to_plot, aes(x = fct_inorder(comp), y = count, fill = prog))+
  geom_bar(stat = "identity")
dev.off()
```

wonder what happens if we get rid of kallisto...
```{r}
to_plot[to_plot == ""] = NA
to_plot_vm <- to_plot %>% filter(!is.na(prog_vm))
colours <- c("#53B400", "#00C094", "#FB61D7")
```

```{r}
png("test.png", units="in", width=15, height=8, res=300)
ggplot(to_plot_vm, aes(x = comp, y = count, fill = prog_vm))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

ok, so at the very least, vast and majiq agree somewhat well. I wonder then, are the general trends the same across all 3 programs (d > w, l > k)?
```{r}
#this ordeer doesn't actually matter, it'll get fixed after group_by and summarize
kallisto_all <- rbind(kallisto_k20dk20w,  kallisto_k40dk40w, kallisto_k60dk60w, kallisto_l20dl20w, kallisto_l40dl40w, kallisto_l60dl60w, kallisto_k20dl20d,kallisto_k40dl40d,kallisto_k60dl60d, kallisto_k20wl20w, kallisto_k40wl40w, kallisto_k60wl60w)

kallisto_all <- kallisto_all %>% 
  group_by(comp) %>% 
  summarize(count = n())%>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(kallisto_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "cadetblue3")
dev.off()
```

```{r}
vast_all <- rbind(vast_k20dk20w, vast_k20dl20d, vast_k20wl20w, vast_k40dk40w, vast_k40dl40d, vast_k40wl40w, vast_k60dk60w, vast_k60dl60d, vast_k60wl60w, vast_l20dl20w, vast_l40dl40w, vast_l60dl60w)

vast_all <- vast_all %>% 
  group_by(comp) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(vast_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "orchid")
dev.off()
```

```{r}
majiq_all <- rbind(majiq_k20dk20w, majiq_k20dl20d, majiq_k20wl20w, majiq_k40dk40w, majiq_k40dl40d, majiq_k40wl40w, majiq_k60dk60w, majiq_k60dl60d, majiq_k60wl60w, majiq_l20dl20w, majiq_l40dl40w, majiq_l60dl60w)

majiq_all <- majiq_all %>% 
  group_by(comp) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(majiq_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "springgreen2")
dev.off()
```



